Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caption to neighborhood-mass relation fig

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{Caption.}
\label{fig:Rn_mc}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for our three
orbits (blue, orange, and red) and for each of the FIRE galaxies considered
here --- m12i, m12f, and m12m ({\em left}, {\em center}, and {\em right}
panels, respectively). Given the $z$ offset for a cluster of mass $m_c$
computed in Figure~\ref{fig:cluster_offset}, we convert this to a chord length
using the result from Figure~\ref{fig:range_deltaphi} and plot as a solid blue
line. We interpret this chord length as the ``neighborhood'' around the
cluster, i.e. the distance from the cluster one could go before the $J_z$
error induced by our midplane effect is comparable to the intrinsic action
dispersion of the cluster. When the $z$ offset is larger than the maximum
range in Figure~\ref{fig:range_deltaphi}, we report the maximum chord length
($2\times8.2\,\kpc$). We aso report the same procedure but using the
$\pm1\sigma$ lines from Figure~\ref{fig:range_deltaphi}, which we plot here as
dashed lines. For the medium- and high-$J_z$ orbits (orange and red), the
neighborhood is quite large and thus the effect is negligible. However, for
the low-$J_z$ orbit (blue), which is closest to the orbits of nearby open
clusters (see Table~\Gus{x}), the neighborhood is only a few hundred $\pc$ for
low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}
